How to we handle the categorical predictors?

### 2021-11-15 understanding_mm_special.rmd
Autocommit

```{r unbalanced_sim, echo=TRUE}
N <- 100
quant <- seq(0,1,length.out=50)
## Betas
b0 <- 10
b_age <- 0.8
b_jew <- 1
b_muslim <- 0.4
b_male <- 2
b_male_jew <- 0.7
b_male_muslim <- 0.2
betas <- c(b0, b_age, b_jew, b_muslim, b_male, b_male_jew, b_male_muslim)

@@

>>>>

```{r unbalanced_sim, echo=TRUE}
N <- 100
quant <- seq(0,1,length.out=100)
## Betas
b0 <- 10
b_age <- 0.8
b_jew <- 1
b_muslim <- 0.4
b_male <- 2
b_male_jew <- 0.7
b_male_muslim <- 0.2
betas <- c(b0, b_age, b_jew, b_muslim, b_male, b_male_jew, b_male_muslim)

@@

```{r}
varpred(unbalanced_mod, "age", at=list(age=mean(unbalanced_df$age)))
emmeans(unbalanced_mod, specs=~age, weights="proportional", nesting=NULL)
```
